Brief notes on erosion

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

The co-PI of this project is {\bf Nick Moore}.  Since 2014, Dr.~Moore
has been an Assistant Professor in the Department of Mathematics at
Florida State University.  He is also a Research Associate in FSU's
Geophysical Fluid Dynamics Institute. \todo[inline]{A bit more}

>>>>

The co-PI of this project is {\bf Nick Moore}.  Since 2014, Dr.~Moore
has been an Assistant Professor in the Department of Mathematics at
Florida State University.  He is also a Research Associate in FSU's
Geophysical Fluid Dynamics Institute. 
Dr.~Moore received his Ph.D.~in 2010 in Mathematics at the University of North Carolina, Chapel Hill. He was a postdoctoral researcher at the Courant Institute of Mathematical Sciences from 2010-2014 working with Michael Shelley and others. His expertise includes modeling dynamic interactions between fluids and structures, especially in geophysically and biologically motivated settings.
